Curve Average \\ {\large Project 3 for class CS6491 Computer Graphics}

### 2015-11-01 paper/paper.tex
added short result chapter and example images

\section{Results}

\section{Future work}

>>>>

\section{Results}
In conclusion, we are able to trace the average curve of two piecewise hermite interpolated curves in real-time, whereat the user defines the control points by dragging them around.
We presented ideas on how to detect if the two control curves are compatible or not.
Furthermore, we showed different ways on how to display the average curve, using line segments to the closest projections, circular arcs or the inflation tube.

\section{Future work}
This work can easily be extended to any kind of input curve and any number of control points.
Also more freedom for the user to specify the input curve, like editing the velocities, might be helpful for specific applications.

% EXAMPLES
\begin{figure*}
	\centering
		\includegraphics[scale=0.4]{images/Result1.png}
		\includegraphics[scale=0.4]{images/Result2.png}
	\caption{Example 1: a bow}
	\label{fig:Result1}
\end{figure*}
\begin{figure*}
	\centering
		\includegraphics[scale=0.4]{images/Result3.png}
	\caption{Example 2: a waterslide}
	\label{fig:Result3}
\end{figure*}
\begin{figure*}
	\centering
		\includegraphics[scale=0.5]{images/Result4.png}
		\includegraphics[scale=0.5]{images/Result5.png}
	\caption{Example 3: extreme cases and non-compatibility detection}
	\label{fig:Result4}
\end{figure*}
